# Fundamentals of Python

```{r echo=FALSE}
# ensures embedding with `xfun::embed_file` works.
# include only once before you embed some file.
xfun::pkg_load2(c("htmltools", "mime"))
```


Let's get started with the course contents!
In this first part of the course, we will give an introduction to programming with Python.
You will learn the fundamentals of Python and apply your new skills in small exercises.
After you got up to speed, we will have an introduction to Jupyter Notebooks --- an interactive environment to write, execute, and comment, and share Python code and results.

## Lecture Notes

::: slide-deck
**Part 2: Fundamentals of Python**

::: slides

```{r echo=FALSE}
xfun::embed_file("slides/Lecture_2_Intro_Python.pdf", text = "Slides")
```
:::
:::


## Application Exercise During the Course

:::: application-exercise
**Vectors, Loops, and Functions**

Please open Google Colab for this exercise through the following link.
After opening the Google Colab instance, save a copy to your own Google drive.
That's how you will retain your copy with your own code.

::: source
[Exercise Template on Google Colab](https://colab.research.google.com/github/coding-intro/intro-python-2023-07/blob/main/notebooks/Part%202%20Fundamentals%20of%20Python/Exercises_Lecture2.ipynb){target="_blank"}
:::

<!-- Note: Comment the solutions if you don't want to show them. -->
<!-- After the course unit, you can uncomment them -->

<!-- ::: source -->
<!-- [Solution](insert-link-here){target="_blank"}  -->
<!-- ::: -->
:::



## Additional Application Exercises for Self-Study

Ready for some more hands-on exercises? Here you go --- four coding challenges that you can solve after our workshop.

:::: application-exercise
**More Advanced Loops, Strings, and Lists**


::: source
[Exercise Template on Google Colab](https://colab.research.google.com/github/coding-intro/intro-python-2023-07/blob/main/notebooks/Part%202%20Fundamentals%20of%20Python/Homework_Lecture_2.ipynb){target="_blank"} 
:::

<!-- Note: Comment the solutions if you don't want to show them. -->
<!-- After the course unit, you can uncomment them -->

::: solutionlink
[Solution](https://colab.research.google.com/github/coding-intro/intro-python-2023-07/blob/main/notebooks/Part%202%20Fundamentals%20of%20Python/Solutions_Homework_2.ipynb){target="_blank"}
:::
:::

